Experiments

### 2020-11-29 StateOfPractice/Methodology/Experiments.tex
updated modifiability experiment introduction, added Clements

Parnas's definition of likely changes has informed this analysis: ``If the system is required to be easy to change, the requirements should contain a definition of the areas that are considered likely to change. You cannot design a system so that everything is equally easy to change. Programmers should not have to decide which changes are most likely'' \cite{parnas1986rational}.

>>>>

Parnas and Clements' definition of likely changes has informed this analysis: ``If the system is required to be easy to change, the requirements should contain a definition of the areas that are considered likely to change. You cannot design a system so that everything is equally easy to change. Programmers should not have to decide which changes are most likely'' \cite{parnas1986rational}.
